Reproducibility in Plant Pathology

### 2024-08-07 README.rmd
update repo badge and clean up website files

# Reproducibility in Plant Pathology
<!-- badges: start -->
![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges: end -->

>>>>

# Reproducibility in Plant Pathology
<!-- badges: start -->
![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Inactive – The project has reached a stable, usable state but is no longer being actively developed; support/maintenance will be provided as time allows.](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
<!-- badges: end -->
